\documentclass[a4paper,11pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{xcolor}

\setstretch{1.05}
\pagenumbering{gobble}

\setlist[itemize]{itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt, leftmargin=20pt, labelsep=6pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}

\begin{center}
{\fontsize{16}{18}\selectfont \textbf{GURU PRASAD M}} \\
\vspace{4pt}
Chennai, India \quad \textbullet \quad +91-9480246319 \quad \textbullet \quad \href{mailto:guruprasad4790@gmail.com}{guruprasad4790@gmail.com}
\end{center}

\vspace{-8pt}

\section*{SUMMARY}

Senior Software Engineer with 14+ years of experience in distributed systems and real-time telecom platforms. Strong experience in diagnosing complex system issues, including regression and integration failures, and performing live debugging across component boundaries. Experienced in handling system instability, triaging issues in production environments, and driving resolution through cross-team coordination.

\vspace{2pt}

\section*{CORE SKILLS}

\noindent\textbf{Languages:} C++, Python, SQL, Shell \\
\textbf{Systems:} Distributed Systems, Real-Time Processing, Linux \\
\textbf{Protocols:} IMS, SIP, Diameter \\
\textbf{Tools:} Redis, Docker, Jenkins, Git \\
\textbf{Practices:} Debugging, Incident Handling, System Stability, Production Support \\

\vspace{-8pt}

\section*{PROFESSIONAL EXPERIENCE}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Technical Lead} — Xoriant (Cisco UCSM) & Aug 2024 -- Feb 2026 \\
\end{tabular*}

\noindent\hspace{4pt}
\begin{itemize}
\item Diagnosed and resolved defects across server and networking components, including regression issues introduced by new feature integrations.
\item Performed live debugging in complex systems to identify root causes across component boundaries.
\item Investigated system instability issues and supported resolution of production incidents.
\item Led a team of 9 engineers while contributing hands-on to debugging and issue resolution.
\item Handled escalations by coordinating across teams to drive fixes and stabilize releases.
\end{itemize}

\vspace{2pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Independent Project} — Execution and Delivery & Mar 2026 -- Apr 2026 \\
\end{tabular*}

\noindent\hspace{4pt}
\begin{itemize}
\item Executed a time-bound on-site project involving diagnosis and rebuild of a lime-based wall system, coordinating across multiple stakeholders to meet fixed deadlines.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Senior Software Engineer} — Cloudtern (Pareteum MVNE) & Dec 2020 -- Apr 2024 \\
\end{tabular*}

\begin{itemize}
\item Designed Redis-based session handling to enable stateless processing in real-time systems, improving resilience and scalability.
\item Improved system flexibility through JSON-based configuration management.
\item Diagnosed and resolved defects in billing and session handling systems through root cause analysis.
\item Built REST-based mechanisms for dynamic configuration updates in running systems.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Technical Lead} — HCL (Cisco / Synamedia) & Nov 2018 -- Jul 2020 \\
\end{tabular*}

\begin{itemize}
\item Optimized a processing system, reducing AWS storage and request overhead.
\item Provided on-call support and resolved high-priority issues in live environments.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{R\&D Engineer} — Nokia Networks (IMS Core Platform) & Aug 2014 -- Oct 2018 \\
\end{tabular*}

\begin{itemize}
\item Developed and enhanced components in a large-scale distributed IMS core system.
\item Implemented protocol-level enhancements including location tracking and access class updates.
\item Improved system efficiency by redesigning processing logic.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Software Engineer} — CSG International (Singleview) & Oct 2013 -- Aug 2014 \\
\end{tabular*}

\begin{itemize}
\item Maintained telecom billing systems and resolved defects in production environments.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{R\&D Software Engineer} — Aricent (ComverseONE) & Sept 2011 -- Oct 2013 \\
\end{tabular*}

\begin{itemize}
\item Enhanced Diameter modules and implemented charging features for telecom services.
\end{itemize}

\vspace{4pt}

\section*{EDUCATION}

\noindent\textbf{B.E. Computer Science and Engineering} \hfill 2011 \\
Sir M. Visvesvaraya Institute of Technology

\end{document}