\documentclass[a4paper,11pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{xcolor}

\setstretch{1.05}
\pagenumbering{gobble}

\setlist[itemize]{itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt, leftmargin=20pt, labelsep=6pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}

\begin{center}
{\fontsize{16}{18}\selectfont \textbf{GURU PRASAD M}} \\
\vspace{4pt}
Chennai, India \quad \textbullet \quad +91-9480246319 \quad \textbullet \quad \href{mailto:guruprasad4790@gmail.com}{guruprasad4790@gmail.com}
\end{center}

\vspace{-8pt}

\section*{SUMMARY}

Technical Lead with 14+ years of experience in distributed systems and real-time telecom platforms. Experienced in designing and evolving system components, improving reliability and maintainability, and leading teams through complex problem-solving. Strong background in debugging, cross-component analysis, and delivering stable systems in production environments.

\vspace{2pt}

\section*{CORE SKILLS}

\noindent\textbf{Languages:} C++, Python, SQL, Shell \\
\textbf{Systems:} Distributed Systems, Real-Time Processing, Linux \\
\textbf{Protocols:} IMS, SIP, Diameter \\
\textbf{Tools:} Redis, Docker, Jenkins, Git \\
\textbf{Practices:} System Design, Debugging, Incident Handling, System Stability \\

\vspace{-8pt}

\section*{PROFESSIONAL EXPERIENCE}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Technical Lead} — Xoriant (Cisco UCSM) & Aug 2024 -- Feb 2026 \\
\end{tabular*}

\noindent\hspace{4pt}
\begin{itemize}
\item Led debugging and resolution of defects across server and networking components, including regression issues from feature integrations.
\item Performed live debugging in complex systems to identify root causes across component boundaries.
\item Investigated system instability and supported resolution of production incidents.
\item Led a team of 9 engineers, driving issue resolution and coordinating cross-team fixes.
\item Contributed to improving system stability during maintenance and release cycles.
\end{itemize}

\vspace{2pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Independent Project} — Execution and Delivery & Mar 2026 -- Apr 2026 \\
\end{tabular*}

\noindent\hspace{4pt}
\begin{itemize}
\item Executed a time-bound on-site project involving diagnosis and rebuild of a lime-based wall system, coordinating across multiple stakeholders to meet fixed deadlines.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Senior Software Engineer} — Cloudtern (Pareteum MVNE) & Dec 2020 -- Apr 2024 \\
\end{tabular*}

\noindent\hspace{4pt}
\begin{itemize}
\item Designed Redis-based session handling to enable stateless processing in real-time systems, improving scalability and maintainability.
\item Improved system flexibility through JSON-based configuration management.
\item Diagnosed and resolved defects in billing and session handling systems.
\item Built REST-based mechanisms for dynamic configuration updates in running systems.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Technical Lead} — HCL (Cisco / Synamedia) & Nov 2018 -- Jul 2020 \\
\end{tabular*}

\begin{itemize}
\item Redesigned a processing system to reduce AWS storage and request overhead.
\item Provided on-call support and resolved high-priority issues in live environments.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{R\&D Engineer} — Nokia Networks (IMS Core Platform) & Aug 2014 -- Oct 2018 \\
\end{tabular*}

\begin{itemize}
\item Developed and enhanced charging-related features within a large-scale IMS core system, working across CSCF components.
\item Implemented protocol-level features including location tracking and access class updates.
\item Improved system efficiency by redesigning processing logic.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Software Engineer} — CSG International (Singleview) & Oct 2013 -- Aug 2014 \\
\end{tabular*}

\begin{itemize}
\item Maintained telecom billing systems and resolved defects in production environments.
\end{itemize}

\vspace{4pt}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{R\&D Software Engineer} — Aricent (ComverseONE) & Sept 2011 -- Oct 2013 \\
\end{tabular*}

\begin{itemize}
\item Enhanced Diameter modules and implemented charging features for telecom services.
\end{itemize}

\vspace{4pt}

\section*{EDUCATION}

\noindent\textbf{B.E. Computer Science and Engineering} \hfill 2011 \\
Sir M. Visvesvaraya Institute of Technology

\end{document}